\documentclass{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[francais]{babel}
\usepackage{xargs}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage[svgnames]{xcolor}

\usepackage{array}

\usepackage{tikz}
\usetikzlibrary{patterns}
\usepackage{caption}
\usepackage{subcaption}

\input{/home/mnattaf/Documents/input_latex/usepackage.tex}
\input{/home/mnattaf/Documents/input_latex/newcommand.tex}

\newtheorem{Th}{Theorem}
\newtheorem{Lem}{Lemma}

\begin{document}

We want to prove that the following set of inequalities: 
\begin{align}
z_{ie} \le z_{ie-1}+(1-\sum_{j\neq i}(z_{je}-z_{je-1})) & \forall
i,\ \forall e \label{eq1}\\
z_{ie} \le z_{ie-1}+(1-\sum_{j\neq i}(z_{je-1}-z_{je})) & \forall
i,\ \forall e\label{eq2}\\
z_{ie} \ge z_{ie-1}-(1-\sum_{j\neq i}(z_{je}-z_{je-1})) & \forall
i,\ \forall e\label{eq3}\\
z_{ie} \ge z_{ie-1}-(1-\sum_{j\neq i}(z_{je-1}-z_{je})) & \forall
i,\ \forall e\label{eq4}
\end{align}
express the property that an event $e$ cannot corresponds to either
two task starts, or two task ends, or a task start and a task end.

First, we prove that if $e$ correspond to only one task start
(resp. end) then the inequalities are verified.

Suppose then that event $e$ is the start of task $i$. Inequality
(\ref{eq1}) and (\ref{eq4}) can be rewritten as:
\begin{align}
\sum_{i\in A}(z_{ie}-z_{ie-1}) \le 1 &\forall e\label{eq5}\\
\sum_{i\in A}(z_{ie-1}-z_{ie}) \le 1 &\forall e\label{eq6}
\end{align}
where $A=\{1,\dots,n\}$ is the set of all tasks. Clearly, these
inequalities are satisfied.

Now we prove that inequality (\ref{eq2}) is verified $\forall j\in
A$. For task $i$, we have: $1 \le 0+1-0 \Rightarrow 1 \le 1$. For the
other tasks, the inequality gives $z_{je}-z_{je-1}=0 \le 1+1
\Rightarrow 0\le 2$. Thus, inequality (\ref{eq2}) is satisfied.

Apply inequality (\ref{eq3}) on task $i$ gives $1 \ge 0 - 1 +0
\Rightarrow 1 \ge 1$ which is true. For the other tasks, we have
$z_{je}-z_{je-1}=0 \ge -1+1 \Rightarrow 0\le 0$. Therefore,
(\ref{eq3}) is satisfied and if $e$ correspond to the start of one
task only, inequalities (\ref{eq1})--(\ref{eq4}) are verified. We can
prove in a similar way that if $e$ is the end of only one task these
inequalities hold also.

Now, we have to prove that if an event $e$ corresponds to either two
task starts, or two task ends, or a task start and a task end then the
inequalities are not satisfied. First, we recall that:
\[(\ref{eq1})+(\ref{eq4}) \Rightarrow -1 \le \sum_{i\in A}(z_{ie}-z_{ie-1}) \le 1\]
Therefore, we only have three cases to consider: 
\begin{itemize}
\item $e$ correspond to $l+1$ starts and to $l$ ends ($l\ge 1$)
\item $e$ correspond to $l$ starts and to $l+1$ ends ($l\ge 1$)
\item $e$ correspond to $l$ starts and to $l$ ends ($l\ge 1$)
\end{itemize}

For the first case, we denote by $i_1,\dots,i_{l+1}$
(resp. $j_1,\dots,j_l$) the tasks starting (resp. ending) at event
$e$. Then, considering task $j_1$ and inequality (\ref{eq3}), we have
$z_{j_1e} \ge z_{j_1e-1} -1 - \sum_{k=j_2}^{j_l}(z_{ke-1}-z_{ke})+
\sum_{k=i_1}^{i_{l+1}}(z_{ke}-z_{ke-1}) \Rightarrow 0 \ge
1-1-l+1+l+1\Rightarrow 0\ge 2$ and then inequality (\ref{eq3}) is not
satisfied.

Similarly, for the second case, we denote by $i_1,\dots,i_{l}$
(resp. $j_1,\dots,j_{l+1}$) the tasks starting (resp. ending) at event
$e$. Then, considering task $i_1$ and inequality (\ref{eq2}), we have
$z_{i_1e} \le z_{i_1e-1}+1 - \sum_{k=j_1}^{j_{l+1}}(z_{ke-1}-z_{ke})+
\sum_{k=i_2}^{i_{l}}(z_{ke}-z_{ke-1}) \Rightarrow 1 \le
0+1-l-1+l-1\Rightarrow 1\le 0$ and then inequality (\ref{eq2}) is not
satisfied.

Finallly, for the last case, we denote by $i_1,\dots,i_{l}$
(resp. $j_1,\dots,j_{l}$) the tasks starting (resp. ending) at event
$e$. Then, considering task $j_1$ and inequality (\ref{eq3}), we have
$z_{j_1e} \ge z_{j_1e-1} -1 - \sum_{k=j_2}^{j_{l}}(z_{ke-1}-z_{ke})+
\sum_{k=i_1}^{i_{l}}(z_{ke}-z_{ke-1}) \Rightarrow 0 \ge
1-1+l-l+1\Rightarrow 0\ge 1$ and then inequality (\ref{eq3}) is not
satisfied.

Therefore, inequalities (\ref{eq1})--(\ref{eq4}) express the property
that an event $e$ cannot corresponds to either two task starts, or two
task ends, or a task start and a task end.
\end{document}
